### 2020-05-23 Manuscript/manuscript.tex
add reviewer acknowledgements and (CC BY 4.0) license info

Many participants in the Nordic Paleomagnetism Workshop have contributed to the compilation and evaluation of the pole list utilized herein. Particular acknowledgement goes to David Evans for maintaining and distributing the compiled pole lists as well as additional efforts of Lauri Pesonen in maintaining the Paleomagia database \citep{Veikkolainen2014a}. GPlates, and in particular the pyGPlates API, was utilized in this work \citep{Muller2018b}. Figures were made using Matplotlib \citep{Hunter2007a} in conjunction with cartopy \citep{Met-Office2010a} and pmagpy \citep{Tauxe2016a} within an interactive Python environment \citep{Perez2007a}. This work was supported by NSF CAREER Grant EAR-1847277 awarded to N.L.S.-H. The code, data, and reconstructions used in this paper are openly available in this repository: \url{https://github.com/Swanson-Hysell-Group/Laurentia_Paleogeography}.

>>>>

Many participants in the Nordic Paleomagnetism Workshop have contributed to the compilation and evaluation of the pole list utilized herein. Particular acknowledgement goes to David Evans for maintaining and distributing the compiled pole lists as well as additional efforts of Lauri Pesonen in maintaining the Paleomagia database \citep{Veikkolainen2014a}. GPlates, and in particular the pyGPlates API, was utilized in this work \citep{Muller2018b}. Figures were made using Matplotlib \citep{Hunter2007a} in conjunction with cartopy \citep{Met-Office2010a} and pmagpy \citep{Tauxe2016a} within an interactive Python environment \citep{Perez2007a}. The manuscript benefited from reviews from Athena Eyster, David Evans, and Lauri Pesonen as well as discussions with Francis Macdonald. This work was supported by NSF CAREER Grant EAR-1847277 awarded to N.L.S.-H. The chapter text as well as code, data, and reconstructions used in this paper are openly available and licensed for any form of reuse (CC BY 4.0) with attribution in this repository: \url{https://github.com/Swanson-Hysell-Group/Laurentia_Paleogeography}.
